Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-19 talk_ucl_cdt_200622/introduction.tex
First intro slide

\begin{frame}
	\frametitle{Tritium Breeding in ICF Reactors}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Dimensionality Reduction}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Project Background}
	Nuclear fusion -- the energy of the future!
    \vspace{10pt}
	\begin{itemize}
	    \item Must produce and contain an extremely hot and dense plasma
	    \begin{itemize}
		    \item Magnetic Confinement Fusion (MCF): toroidal circulation
		    \item Inertial Confinement Fusion (ICF): spherical compression
		\end{itemize}
		\vspace{10pt}
		\item Modern designs require enriched Hydrogen fuel of two varieties:
	    \begin{itemize}
		    \item Deuterium ($^2$H) -- abundant in naturally-sourced water
		    \item Tritium ($^3$H) -- extremely rare, but can be produced \textit{in-reactor}
		\end{itemize}
	\end{itemize}
	\vspace{10pt}
	\centering{\includegraphics[height=3cm]{icf_diagram}}
\end{frame}

@@

%\begin{frame}
%	\frametitle{Dimensionality Reduction}
%	\begin{itemize}
%		\item % TODO
%	\end{itemize}
%\end{frame}
